---
output: github_document
---

<!-- README.md is generated from README.Rmd. Build with build_readme() -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "50%"
)
```

# Evaluating TK Models: AquaTK Package

The AquaTK package (pronounced "aquatic") is the supporting material for the publication:

_Evaluating Toxicokinetic Compartmental Models as
Predictors of Internal Concentration in
Environmentally Relevant Species_ (Collins 2023)

The package makes toxicokinetic data for a variety of aquatic species 
publicly available and easily accessible.

## Installation
The development version of the AquaTK package is hosted on 
[GitHub](https://github.com/J-Collins1294/AquaTK) and 
is installed with the R command:

```{r install}
# install.packages("devtools")
# devtools::install_github("J-Collins1294/AquaTK")
```

## Examples
Load the _combined_ dataset (both fish and daphnia) with: 

```{r example}

library(AquaTK)

df <- AquaTK::combined

```

The data for a specific chemical in the dataset is extracted and plot 
as a function of the exposure time: 

```{r plot-example}

df <- AquaTK::daphnia
df_atrazine <- df[grepl("Atrazine", df$NAME),]

plot(
  df_atrazine$EXPOSURE,
  df_atrazine$INTERNAL,
     xlab = "Exposure time (hours)",
     ylab = "Internal Concentration (ug/L)")


```

## Publication
Please cite the package with `citation("AquaTK")`.

## Documentation 
For more comprehensive details on how to use this library, 
or descriptions of the processing steps, 
please see the vignette 
or run the following command:

```{r help}

??AquaTK::fish

```

